Mermory-efficient Fujisaki-Okamoto transformation

### 2024-05-22 lattices/compact-fo-using-mac/manuscript/main.tex
QUERY *

    % TODO: Bound the probabiolity P[QUERY*]

    % TODO: game 3 can be simulated by a OW-CPA adversary

>>>>

    we can bound $P[\operatorname{QUERY}\ast]$ by constructing an OW-CPA adversary that simulates game 3 for a OW-PCVA adversary as a sub-routine. After the OW-PCVA adversary halts, the OW-CPA adversary checks through the tape of the hash oracle. Since the encryption routine is deterministic, if $m^\ast$ exists in the hash oracle tape, then it can be identified for sure. In other words, if $m^\ast$ has been queried by the OW-PCVA sub-routine, then the OW-CPA adversary can be guaranteed to win its game

    \begin{equation*}
        P[\operatorname{QUERY}\ast] = \epsilon_\text{OW-CPA}
    \end{equation*}

    Finally, game 3 can be simulated by the OW-CPA
